Notes

### 2022-02-14 notes.tex
Start paper

\margintoc[*-2]

\section{Questions}

Here are some questions.

@@

  \item Why is it that \(k(\cdot, t) \notin \mathcal K(L^2)\)?

  \item We are assuming that \(\beta, \tau\) and \(\sigma^2\) are independent? Independent given \(Y\) and/or \(X\)?

  \item How many samples is it usually enough to successfully predict a relatively simple model? What about the execution time?

  \item How to set a sensible value for \(g\) and \(b_0\)? Cross-validation?

  \item Which MCMC sampling algorithm should we use?

  \item Can we ignore the posterior on \(\sigma^2\) and treat it as a nuisance parameter?

  \item \textbf{How to include the case in which} \(\bm{\mathds EX(t)\neq 0}\) \textbf{and/or} \(\bm{\mathds EY\neq 0}\)? Do we add a term \(\mu\) in the model and impose a prior on it as well? How would we treat the terms \(X_i(t_j) - m(t_j)\) resulting from \(\Psi^{-1}_{X_i}(k(\cdot, t_j))\)? Can we just subtract the sample mean to every sample trajectory and response and work with our current model?

  \item How do we get an estimate of the parameters given the posterior distribution?

  \item How do we try the algorithm in a more realistic setting? Which is the standard error measure for the latent parameters?

@@

\newpage

@@

Following a Bayesian approach, we can set a prior distribution on the parameters, such as:
\begin{align*}
  f(\sigma^2)              & \propto 1/\sigma^2,                                                     \\
  \tau                     & \sim \mathscr U([0, 1]^p),                                              \\
  \beta\mid \tau, \sigma^2 & \sim \mathcal N(b_0, g\sigma^2(\mathcal X_\tau' \mathcal X_\tau)^{-1}),
\end{align*}
where\sidenote[][*1]{This is because of the correspondence between \(k(\cdot, t_j)\) and \(X(t_j)\), which becomes relevant when plugging the approximation~\eqref{eq:alpha} into the model~\eqref{eq:model_lin}.}
\(\mathcal X_\tau(i, j)=X_i(t_j)\). The prior on \(\beta\) is known as Zellner's \(g\)-prior owing to the main hyperparameter \(g\in \R^+\), which controls the confidence we have in the initial estimate \(b_0 \in \R^p\) for the true value of the coefficients. The choice of a non-informative improper prior for \(\sigma^2\) is of course subject to change. All in all, the prior distribution for the parameters becomes
\begin{equation}
  \label{eq:prior}
  \pi(\theta) = \pi(\beta, \tau, \sigma^2) = \pi(\beta \mid \tau, \sigma^2)\pi(\tau \mid \sigma^2)\pi(\sigma^2).
\end{equation}

@@

\subsubsection{Resources for MCMC methods}

Some resources on MCMC methods in Python are:

\begin{enumerate}
  \item \href{https://www.tweag.io/blog/2019-10-25-mcmc-intro1/}{A step-by-step tutorial}
  \item \href{http://www.stat.columbia.edu/~gelman/research/published/nuts.pdf}{NUTS sampler}
  \item \href{https://github.com/michaelnowotny/pyjags}{pyjags}
  \item \href{https://www.cdslab.org/paramonte/index.html}{ParaMonte}
  \item \href{https://github.com/prmiles/pymcmcstat}{pymcmcstat}
  \item \href{https://docs.pymc.io/}{\textbf{PyMC3}}
  \item \href{https://mc-stan.org/}{Stan}
  \item \href{https://emcee.readthedocs.io/en/stable/tutorials/quickstart/#quickstart}{\textbf{emcee}}
\end{enumerate}

@@

  \item Derive Bayesian estimates of the support and/or the coefficient function by minimizing a loss function integrated with respect to the posterior distribution, as done in \sidetextcite[*-2]{grollemund2019bayesian}. In particular, it is worth exploring the \textit{prior and posterior predictive probabilities} of the parameters to gain insight into them (as explained \href{https://en.wikipedia.org/wiki/Bayesian_inference#Bayesian_prediction}{here}).

>>>>

\margintoc[*-7]

\section{TODO}

@@

\textbf{ANSWER}: Continuous linear functionals are only obtained by integrating a coefficient function against $x(t)$ (Riesz-Fisher), and it is not possible to select a $\beta(t)$ that produces finite linear combinations of the process after integrating.

\item \(\alpha(t)=E [X(t)U]\) is the correlation/covariance of $X$ and $U$ (Berrendero et al. 2019, 2020), if we assume that $E[X(t) \varepsilon]=0$. Moreover, are we assuming $E[(X(t) - m(t))U)]=0$?

\item Since the RMSE is measured on the same scale, with the same units as y, one can expect 68\% of the y values to be within 1 RMSE — given the data is normally distributed.

@@

@@

Following a Bayesian approach, we can set a prior distribution on the parameters, such as:
\begin{align*}
  f(\sigma^2)              & \propto 1/\sigma^2,                                                     \\
  \tau                     & \sim \mathscr U([0, 1]^p),                                              \\
  \beta\mid \tau, \sigma^2 & \sim \mathcal N(b_0, g\sigma^2(\mathcal X_\tau' \mathcal X_\tau)^{-1}),
\end{align*}
where\sidenote[][*1]{This is because of the correspondence between \(k(\cdot, t_j)\) and \(X(t_j)\), which becomes relevant when plugging the approximation~\eqref{eq:alpha} into the model~\eqref{eq:model_lin}.}
\(\mathcal X_\tau(i, j)=X_i(t_j)\). The prior on \(\beta\) is known as Zellner's \(g\)-prior owing to the main hyperparameter \(g\in \R^+\), which controls the confidence we have in the initial estimate \(b_0 \in \R^p\) for the true value of the coefficients. The choice of a non-informative improper prior for \(\sigma^2\) (known as Jeffreys prior) is of course subject to change. All in all, the prior distribution for the parameters becomes
\begin{equation}
  \label{eq:prior}
  \pi(\theta) = \pi(\beta, \tau, \sigma^2) = \pi(\beta \mid \tau, \sigma^2)\pi(\tau \mid \sigma^2)\pi(\sigma^2).
\end{equation}

@@

\subsubsection{Probabilistic programming in Python: PyMC3}

See \sidetextcite[*0]{salvatier2016probabilistic}.

@@

  \item Derive Bayesian estimates of the support and/or the coefficient function by minimizing a loss function integrated with respect to the posterior distribution, as done in \sidetextcite[*-2]{grollemund2019bayesian}. In particular, it is worth exploring the \textit{prior and posterior predictive probabilities} of the parameters to gain insight into them (as explained \href{https://en.wikipedia.org/wiki/Bayesian_inference#Bayesian_prediction}{here} and illustrated \href{https://docs.pymc.io/en/stable/pymc-examples/examples/diagnostics_and_criticism/posterior_predictive.html}{here}).
